---
title: "Project assignment NumbeoR"
author: "Elvir Ibrahimovic & Svetislav Bratic"
date: "29 9 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Project Description




# Loading the required libraries
```{r}
library("tidyverse")

library(DBI)                           # for PostgreSQL
library(RPostgreSQL)                   # for PostgreSQL

library("jsonlite")                    # JSON files
library("rjson")
```


# Setup of the PostgreSQL database
## Establishing conntection to PostgreSQL

```{r}
pw ="[placceholder]"

# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL") 

# creates a connection to the postgres database; "con" is used to connect to the database
con <- dbConnect(drv, dbname = "NumbeoR",
                 host = "localhost", port = 5432,
                 user = "postgres", password = pw)

# removes the password
rm(pw)
```
## Creation of database
Please create a database in PostgreSQL. Name it "NumbeoR".


## Creation of tables
```{sql connection=con, eval=FALSE}
CREATE TABLE cost_of_living (
    "Year" integer,                                   -- Year
    "Country" text,                                   -- Country
    "Cost of Living Index" numeric,                   -- Cost of Living Index
    "Rent Index" numeric,                             -- Rent Index
    "Cost of Living Plus Rent Index" numeric,   
    "Groceries Index" numeric,                   
    "Restaurant Price Index" numeric,                  
    "Local Purchasing Power Index" numeric                        
);

CREATE TABLE crime (
    "Year" integer,                                   -- Year
    "Country" text,                                   -- Country
    "Crime Index" numeric,              
    "Safety Index" numeric
);

CREATE TABLE health_care (
    "Year" integer,                                   -- Year
    "Country" text,                                   -- Country
    "Health Care Index" numeric,              
    "Health CareExp. Index" numeric                        
);

CREATE TABLE pollution (
    "Year" integer,                                   -- Year
    "Country" text,                                   -- Country
    "Pollution Index" numeric,              
    "Exp Pollution Index" numeric                       
);

CREATE TABLE property_investment (
    "Year" integer,                                   -- Year
    "Country" text,                                   -- Country
    "Price To Income Ratio" numeric,              
    "Gross Rental Yield City Centre" numeric,                        
    "Gross Rental Yield Outside of Centre" numeric,   
    "Price To Rent Ratio City Centre" numeric,                   
    "Price To Rent Ratio Outside Of City Centre" numeric,                  
    "Mortgage As A Percentage Of Income" numeric,                   
    "Affordability Index" numeric                      
);

CREATE TABLE traffic (
    "Year" integer,                                   -- Year
    "Country" text,                                   -- Country
    "Traffic Index" numeric,              
    "Time Index(in minutes)" numeric,                        
    "Time Exp. Index" numeric,   
    "Inefficiency Index" numeric,                   
    "CO2 Emission Index" numeric                        
);


```




# Data import

Reading JSON files
```{r}
json_data_cost_of_living_2017 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/cost-of-living_2017.json")
json_data_cost_of_living_2018 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/cost-of-living_2018.json")
json_data_cost_of_living_2019 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/cost-of-living_2019.json")

json_data_crime_2017 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/crime_2017.json")
json_data_crime_2018 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/crime_2018.json")
json_data_crime_2019 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/crime_2019.json")

json_data_health_care_2017 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/health-care_2017.json")
json_data_health_care_2018 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/health-care_2018.json")
json_data_health_care_2019 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/health-care_2019.json")

json_data_pollution_2017 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/pollution_2017.json")
json_data_pollution_2018 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/pollution_2018.json")
json_data_pollution_2019 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/pollution_2019.json")

json_data_property_investment_2017 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/property-investment_2017.json")
json_data_property_investment_2018 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/property-investment_2018.json")
json_data_property_investment_2019 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/property-investment_2019.json")

json_data_traffic_2017 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/traffic_2017.json")
json_data_traffic_2018 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/traffic_2018.json")
json_data_traffic_2019 <- fromJSON(file="C:/Users/sveti/Desktop/Diverses/GitProjects/NumbeoR/daten/traffic_2019.json")

```

Transform JSON files to  dataframes 
```{r}
df_temp_cost_of_living_2017 <- do.call(rbind.data.frame, json_data_cost_of_living_2017)
df_temp_cost_of_living_2018 <- do.call(rbind.data.frame, json_data_cost_of_living_2018)
df_temp_cost_of_living_2019 <- do.call(rbind.data.frame, json_data_cost_of_living_2019)

df_temp_crime_2017 <- do.call(rbind.data.frame, json_data_crime_2017)
df_temp_crime_2018 <- do.call(rbind.data.frame, json_data_crime_2018)
df_temp_crime_2019 <- do.call(rbind.data.frame, json_data_crime_2019)

df_temp_health_care_2017 <- do.call(rbind.data.frame, json_data_health_care_2017)
df_temp_health_care_2018 <- do.call(rbind.data.frame, json_data_health_care_2018)
df_temp_health_care_2019 <- do.call(rbind.data.frame, json_data_health_care_2019)

df_temp_pollution_2017 <- do.call(rbind.data.frame, json_data_pollution_2017)
df_temp_pollution_2018 <- do.call(rbind.data.frame, json_data_pollution_2018)
df_temp_pollution_2019 <- do.call(rbind.data.frame, json_data_pollution_2019)

df_temp_property_investment_2017 <- do.call(rbind.data.frame, json_data_property_investment_2017)
df_temp_property_investment_2018 <- do.call(rbind.data.frame, json_data_property_investment_2018)
df_temp_property_investment_2019 <- do.call(rbind.data.frame, json_data_property_investment_2019)

df_temp_traffic_2017 <- do.call(rbind.data.frame, json_data_traffic_2017)
df_temp_traffic_2018 <- do.call(rbind.data.frame, json_data_traffic_2018)
df_temp_traffic_2019 <- do.call(rbind.data.frame, json_data_traffic_2019)

```

Transpose dataframes
```{r}
df_cost_of_living_2017 <- as.data.frame(t(df_temp_cost_of_living_2017))
df_cost_of_living_2018 <- as.data.frame(t(df_temp_cost_of_living_2018))
df_cost_of_living_2019 <- as.data.frame(t(df_temp_cost_of_living_2019))

df_crime_2017 <- as.data.frame(t(df_temp_crime_2017))
df_crime_2018 <- as.data.frame(t(df_temp_crime_2018))
df_crime_2019 <- as.data.frame(t(df_temp_crime_2019))

df_health_care_2017 <- as.data.frame(t(df_temp_health_care_2017))
df_health_care_2018 <- as.data.frame(t(df_temp_health_care_2018))
df_health_care_2019 <- as.data.frame(t(df_temp_health_care_2019))

df_pollution_2017 <- as.data.frame(t(df_temp_pollution_2017))
df_pollution_2018 <- as.data.frame(t(df_temp_pollution_2018))
df_pollution_2019 <- as.data.frame(t(df_temp_pollution_2019))

df_property_investment_2017 <- as.data.frame(t(df_temp_property_investment_2017))
df_property_investment_2018 <- as.data.frame(t(df_temp_property_investment_2018))
df_property_investment_2019 <- as.data.frame(t(df_temp_property_investment_2019))

df_traffic_2017 <- as.data.frame(t(df_temp_traffic_2017))
df_traffic_2018 <- as.data.frame(t(df_temp_traffic_2018))
df_traffic_2019 <- as.data.frame(t(df_temp_traffic_2019))

```

# Writing data into PostgreSQL

```{r}
dbWriteTable(con, "cost_of_living", 
             value = df_cost_of_living_2017, append = TRUE, row.names = FALSE)
dbWriteTable(con, "cost_of_living", 
             value = df_cost_of_living_2018, append = TRUE, row.names = FALSE)
dbWriteTable(con, "cost_of_living", 
             value = df_cost_of_living_2019, append = TRUE, row.names = FALSE)

dbWriteTable(con, "crime", 
             value = df_crime_2017, append = TRUE, row.names = FALSE)
dbWriteTable(con, "crime", 
             value = df_crime_2018, append = TRUE, row.names = FALSE)
dbWriteTable(con, "crime", 
             value = df_crime_2019, append = TRUE, row.names = FALSE)

dbWriteTable(con, "health_care", 
             value = df_health_care_2017, append = TRUE, row.names = FALSE)
dbWriteTable(con, "health_care", 
             value = df_health_care_2018, append = TRUE, row.names = FALSE)
dbWriteTable(con, "health_care", 
             value = df_health_care_2019, append = TRUE, row.names = FALSE)

dbWriteTable(con, "pollution", 
             value = df_pollution_2017, append = TRUE, row.names = FALSE)
dbWriteTable(con, "pollution", 
             value = df_pollution_2018, append = TRUE, row.names = FALSE)
dbWriteTable(con, "pollution", 
             value = df_pollution_2019, append = TRUE, row.names = FALSE)

dbWriteTable(con, "property_investment", 
             value = df_property_investment_2017, append = TRUE, row.names = FALSE)
dbWriteTable(con, "property_investment", 
             value = df_property_investment_2018, append = TRUE, row.names = FALSE)
dbWriteTable(con, "property_investment", 
             value = df_property_investment_2019, append = TRUE, row.names = FALSE)

dbWriteTable(con, "traffic", 
             value = df_traffic_2017, append = TRUE, row.names = FALSE)
dbWriteTable(con, "traffic", 
             value = df_traffic_2018, append = TRUE, row.names = FALSE)
dbWriteTable(con, "traffic", 
             value = df_traffic_2019, append = TRUE, row.names = FALSE)
```

# Export Data From PostgreSQL

## R code

```{r}
df_cost_of_living_postgres <- dbGetQuery(con, "SELECT * from cost_of_living")
df_crime_postgres <- dbGetQuery(con, "SELECT * from crime")
df_health_care_postgres <- dbGetQuery(con, "SELECT * from health_care")
df_pollution_postgres <- dbGetQuery(con, "SELECT * from pollution")
df_property_investment_postgres <- dbGetQuery(con, "SELECT * from property_investment")
df_traffic_postgres <- dbGetQuery(con, "SELECT * from traffic")
```

```{r}
```


```{r}
```


```{r}
df_master <- full_join(full_join(full_join(full_join(full_join(df_cost_of_living_postgres, df_crime_postgres, by = c("Country", "Year")),df_health_care_postgres, by = c("Country", "Year")), df_pollution_postgres, by = c("Country", "Year")), df_property_investment_postgres, by = c("Country", "Year")), df_traffic_postgres, by = c("Country", "Year"))


df_master
```


```{r}
filter(df_master, Country=="Italy")
```

## SQL code


# Data Preparation


# Exploratory Data Analysis


# 
